resistanceModelNotesAndy

### 2016-02-01 resistanceModelNotesAndy.Rmd
notes

@@

~ If I would like to get prcc plots in a similar format to my existing plots.
~ get data in form : 
input1, input2, inputN, strategy 
prcc vals,,             indecticide1

>>>>

I got sensitivity::pcc() working for a single strategy.

** 28/1/16 **
~ fixed diagonal axis labels.
~ get sensitivity::pcc() working for all strategies & putting data into format for faceted plots.

** 29/1/16 **

~ why does correctMixDeployProp seem to have an effect in the PRCC of insecticide1 when it shouldn't have any effect outside of mixtures ?

In the plots againts time_to_resistance there is only a bit of a pattern for Mixture1 (time_to_R increaeses between 0.9 & 1 correct deployment).
Points to it being a problem in the PRCC itself.

~~ in setExposure() looks fine, its not applied to insecticide1 or 2

other things it could be :
~~ switched with another var in the call to setExposure
~~ something about how runs are done in sensiAnPaperPart.r 
~~ rows getting reordered within effectOfIndividualInputs.Rmd ?

it is +vely correlated with time to resistance, so better application leads to longer times for resistance to be reached (not sure whether that is waht I would expect ?)

aha PRCC results are influenced by the presence of the other vars, if just do for exposure & deployProp deployProp goes down to 0.2. 
x2 <- x[c('correctMixDeployProp','exposure')]
pcc_res2 <- pcc(x2, y, rank=TRUE)
pcc_res2$PRCC
                       original
correctMixDeployProp  0.2167706
exposure             -0.5248086

I still don't quite understand why an essentially random var is correlated with the output ??

This shows that there's very little correlation between the in & out, for insecticide1
> cor(xy$time_to_resistance0.25,xy$correctMixDeployProp)
[1] 0.003849606

** 1/2/16 **

Checking again on whats happening with correctMixDeployProp

is the correlation similar for mixture1 as it is for insecticide1 ?

could problem be that the inputs are got from a mix run ? shouldn't matter
  treeInput <- listOutMix$input

could it be something to do with the random number seed being disrupted by the extra params ? shouldn't happen

i think the inputs should be identical.

I think it may be a correlation in the analysis.

What I have done is generate inputs for 'male proportion' and 'correct mix deploy'.
Correct mix deployment is not used in the individual insecticide runs, but it is still included as a potential predictor in the PRCC analysis.

In the mixture scenarios 'correct mix deploy' effects exposure ...

exposure is not a single variable in the simulation, but is it used as a single value as a predictor in the sensitivity & prcc analyses ?

aha the exposure predictor is taken from the female AB (actually I think that is OK ??)
although maybe not because it will be reduced by correct deploy and maybe by male (or maybe not ???)

  rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"

correctDeploy has a strong interaction with exposure in mixtures.

When correct deploy is low in mixture runs exposure to AB is much lower because of corresponding exposure to A0 and 0B.

But i think this shouldn't effect single insecticide runs.

Am I sure I'm not mixing up rows somewhere in effectOfIndividualInputs.Rmd ??

I could try setting the values of results for I1 and see if it propogates through.

@@

~ rerun the trees for Ian

~ set 10000 runs going before yoga, but whether extended or normal curtis ?

~ I might be able to do a PRCC of whether mixtures better than sequential (but actually thats what the trees do)

~ I'd like to show prcc on an axis from 0-1 with diff sysmbols for neg & pos. We care about which are most imp. params, not whether they are pos or neg.

~ If I would like to get prcc plots in a similar format to my existing plots. (but may not be space for axis labels)
~ get data in form : 
input1, input2, inputN, strategy 
prcc vals,,             indecticide1
